---
title: "Attempt1"
date: '2022-06-24'
output:
  md_document:
    variant: markdown_github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Problem
A Pythagorean triplet is a set of three natural numbers, $$a < b < c$$, for which, $a^2 + b^2 = c^2$ For example, $3^2 + 4^2 = 9 + 16 = 25 = 5^2$.

There exists exactly one Pythagorean triplet for which a + b + c = 1000.
Find the product abc.

# Solution 1

We know that $a + b + c = 1000$ and that $a^2 + b^2 = c^2$ so therefore:

$$(a + b + c)^2 = a^2 + b^2 + c^2 + 2ab + 2ac + 2bc = 2c^2 + 2ab + 2ac + 2bc = 1,000,000 $$

$$ c^2 + ab + ac + bc = 500,000 $$

$$ a(b+c) + c(b+c) = 500,000 $$
$$ (a+c)(b+c) = 500,000 $$

500,000 has a lot of factors but we can narrow down the candidates by using the fact that $ a < b < c $ which rules out some combinations like 2 and 250,000 since that would imply that $ c = 1$ and $b = 249,000 $ which contradicts the inequality. We also know there is only one solution, so we can start with pairs of multiplicands close to the square root of 500,000 (~707) which has a prime factorization of 5^6*2^5 and will arrive quickly at the answer.

Starting from $ 625 * 800 $ which implies that $ c = 625 + 800 - 1000 = 425$, $ a = 200$, and $b = 375$. This satisfies the inequality, and a quick check will show that it satisfies the other requirements as well

```{r check}
425 + 200 + 375 # should be 1000

425^2 - 200^2 - 375 ^ 2 # should be 0

# product/answer
200*425*375

```
