---
title: "Attempt1"
date: '2022-06-24'
output:
  md_document:
    variant: markdown_github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Problem

2520 is the smallest number that can be divided by each of the numbers from 1 to 10 without any remainder.

What is the smallest positive number that is evenly divisible by all of the numbers from 1 to 20?

# Solution 1

```{r solution}

solution <- function(n) {
  # Essentially, we want to multiply numbers together and remove numbers that are factors of both
  contributions <- 1:n
  running_prod <- 1
  
  for (i in 2:n) {
    # first, if i is 1, that means that this number i has nothing to contribute
    if (contributions[i]==1) { next }
    # for each item in the remaining indices, divide out that factor since it has already been contributed
    j <- i + 1
    while (j <= n) {
      # print(j)
      if (contributions[j] %% contributions[i] ==0 ) { contributions[j] <- contributions[j]/contributions[i]}
      j <- j + 1
    }
    # print(contributions)
    running_prod <- running_prod * contributions[i]
  }
  running_prod
}


# Test
solution(2) # should be 2
solution(3) # should be 6
solution(4) # should be 12
solution(6) # should be 60
solution(8) # should be 840

solution(10) # should be 2520

# Answer
time_start <- Sys.time()
solution(20)
time_end <- Sys.time()

# runtime
time_end - time_start

# Answer
time_start <- Sys.time()
solution(200)
time_end <- Sys.time()

# runtime
time_end - time_start

```

## Time complexity
This algorithm is kinda inefficient because of the sheer number of dividing. It is similar to the sieve of erastothenes so likely nlog(n) time complexity. 